


```{r}
# read CSV file
df <- read.csv("my_data.csv")
```

```{r}
# lets check data
tail(df)
```

```{r}
# now lets check for missing values, if any
sum(is.na(df))

```
There are no missing values

```{r}
# # chceck duolicate data
# sum(duplicated(df))

```


```{r}
# # unique duolicate records
# data <- unique(data)

```

```{r}
# descriptive analysis of data
summary(df)

```

Now lets check the number of unique categorical values per column
```{r}
# Identify character columns
char_cols <- sapply(df, is.character)

# Count unique values for each character column
unique_counts <- sapply(df[, char_cols], function(x) length(unique(x)))

# Combine column names and unique counts into a table
unique_table <- data.frame(column = names(unique_counts), unique_count = unique_counts)

# Print the table
print(unique_table)

```


since country only has one value unique value, so it can not have any affect on the target variable. 
Drop the country column
```{r}
# Assuming your data frame is called "df"
df <- subset(df, select = -c(Country))

```


```{r}
#Now lets check for the information related to data
str(df)

```


now lets explore the distribution of the target vairable i.e. the 'Salary'

```{r}
library(ggplot2)


# Create a count plot
ggplot(df, aes(x = Salary)) +
  geom_bar()


```
```{r}
library(ggplot2)

# Create a data frame with count of each salary range
df_count <- data.frame(table(df$Salary))

# Create a pie chart
ggplot(df_count, aes(x = "", y = Freq, fill = Var1)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar(theta = "y") +
  labs(fill = "Salary") +
  theme_void()

```

 the data is highly biased towards people with lesser salaries


Now lets expolore the relation of Sex with salaries


```{r}
library(ggplot2)

# Create a bar chart with percentages
ggplot(df, aes(x = Salary, fill = Sex)) +
  geom_bar(position = "fill") +
  xlab("Salary") +
  ylab("Percentage") +
  scale_y_continuous(labels = scales::percent)

```

Males have a tendency of higher salaries


Since there are a lot of categorical variables, we will first use ordinal encoding to convert the categories to numbers

```{r}
# Identify categorical columns
categorical_cols <- sapply(df, function(x) is.factor(x) || is.character(x))


# Encode categorical columns using ordinal encoding
for (col in names(df)[categorical_cols]) {
  df[[col]] <- as.integer(factor(df[[col]], ordered = TRUE))
}


```



```{r}
# lets check the data again after encoding
head(df)
```


```{r}

library(ggplot2)

# Create a correlation matrix
correlation_matrix <- round(cor(df), 2)

# Convert the correlation matrix to a data frame
corr_df <- reshape2::melt(correlation_matrix)

# Rename the columns
names(corr_df) <- c("Variable 1", "Variable 2", "Correlation")

# Create a heatmap with numbers
ggplot(corr_df, aes(x = `Variable 1`, y = `Variable 2`, fill = `Correlation`)) +
  geom_tile() +
  geom_text(aes(label = round(Correlation, 2)), color = "white") +
  scale_fill_gradient2(low = "#2E86C1", mid = "white", high = "#F1948A", midpoint = 0) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none")

```





```{r}
corr_df = tail(corr_df, 10)




# select columns "a" and "c"
df_selected <- corr_df[c("Variable 1", "Correlation")]

df_selected <- df_selected[df_selected$'Variable 1' != "Salary", ]

# Sort the dataframe on the basis of correlation
df_sorted <- df_selected[order(-df_selected$Correlation),]
df_sorted
```



```{r}
library(ggplot2)

# Example data frame
df_bar <- data.frame(category = df_sorted$`Variable 1`,
                 values = df_sorted$Correlation)

# Sort the data frame by values in descending order
df_bar <- df_bar[order(-df_bar$values),]

# Create a bar plot
ggplot(df_bar, aes(x = category, y = values)) +
  geom_bar(stat = "identity") +
  xlab("Category") +
  ylab("Values")

```


```{r}
# Sort the dataframe on the basis of the absolute value of correlation
df_selected$Correlation <- abs(df_selected$Correlation)

# Sort the dataframe on the basis of correlation
df_sorted <- df_selected[order(-df_selected$Correlation),]
df_sorted

```




```{r}
library(ggplot2)

# Example data frame
df_bar <- data.frame(category = df_sorted$`Variable 1`,
                 values = df_sorted$Correlation)

# Sort the data frame by values in descending order
df_bar <- df_bar[order(-df_bar$values),]

# Create a bar plot
ggplot(df_bar, aes(x = category, y = values)) +
  geom_bar(stat = "identity") +
  xlab("Category") +
  ylab("Values")
```








Salary is 1 and 2 due to the encoding done earlier.
However, LR requires the target to be 0 and 1 so lets map it
```{r}


# replace 1 with 0 and 2 with 1
df$Salary <- ifelse(df$Salary == 1, 0, 1)


```






```{r}
# Fit logistic regression model
model <- glm(Salary ~ ., data = df, family = "binomial")

# Show model summary
summary(model)

```




















